Understanding the impacts of video-guided activities on parent-child interaction

### 2020-03-19 paper/manuscript.Rmd
final pass with rate

```{r load-exp1-lexical-data, include=F}
e1path = "../parenting_obs_e1/"
load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting
e1_parent_ed = table(d$parent_ed)
#d <- read.csv(paste(e1path,"exp1_conditions2.csv",sep=''))
d = read.csv("exp1_lexical_diversity_data.csv") # old one
d = read.csv("../exp1_lexical_diversityAdd.csv") # with Conversational_Turns

@@

e1_gender = table(e1ld$gender)
```

```{r load-exp1-joint-attention-data, echo=F}
load(paste(e1path,"joint_attention/Exp1_joint_attention_data.RData",sep=''))
d$Condition <- factor(d$Condition, levels = c("con","exp"), labels = c("No Video","Activity Video"))

@@

```{r load-exp2-lexical-data, echo=F}
e2path = "../parenting_obs_e2/"
load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
e2_parent_ed = table(d$parent_ed) # unscaled parent_ed
#d = read.csv("exp2_lexical_diversity_data.csv")
d = read.csv("../exp2_lexical_diversityAdd.csv")

e2data <- d %>%
  mutate(condition = as.factor(condition), 
         gender = as.factor(gender),
         video = as.factor(video))

@@

e2_gender = table(d$gender)
e2_12to18 = nrow(subset(d, Age<1.5)) # wrong now that age is scaled
e2_18to24 = nrow(subset(d, Age>=1.5))
```

@@

### Procedure.
After providing informed consent, parents in the Activity Video condition watched the assigned activity video on a laptop with headphones.
To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played. 
Immediately following the video, each parent-child dyad was provided with the props to complete the video-guided activity that the parent had viewed. 
The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.[^2]
In the No Video condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
They were not given any additional instructions about how to use the props.

@@

A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55,0.91] for number of parent bids for JA; ICC = 0.34 with 95% CI = [-0.11,0.67] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] for number of coordinated JA episodes; ICC = 0.33 with 95% CI = [-0.11,0.67] for total duration of passive JA episodes, and ICC = 0.60 with 95% CI = [0.24,0.82] for total duration of coordinated JA episodes.

@@

For each transcript, the words were lemmatized using ``spacy2`` [@spacy2], and the word *types* (unique words) and *tokens* (total words) were then tallied and the type-token ratio (TTR) calculated as a measure of lexical diversity. 
Although TTR was our preregistered measure of lexical diversity as it has commonly been used, it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity [MTLD; @McCarthy2010]. 
Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here we use the value proposed by @McCarthy2010: 0.720).

@@

# predict word tokens
tokens_mod <- stan_glmer(tokens ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld) 
summary(tokens_mod)
e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 59.5
p_direction(tokens_mod, effects="all") # orchestra 89.7%

# predict word types
types_mod <- stan_glmer(types ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld)
summary(types_mod) # nothing 
p_direction(types_mod, effects="all")

e1_lexdiv <- e1ld %>% group_by(condition) %>%
  summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) 
```

```{r, e1ld-exploratory, echo=F, include=F}
# Predicting lexical diversity based on experimental condition, PAQ, demographics. 
e1model_string = "~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video)"
# only 54 parents completed the EPAQ
modTTRE <- stan_glmer(paste("TTR", e1model_string), data=e1ld)
summary(modTTRE) # conditionexp, RR, genderM, parent_ed 
get_stan_glmer_reporting_values(modTTRE, 'conditionexp') # -.11
p_direction(modTTRE, effects="all") # EL 84.9%, RR 83.3%, parent_ed 91.7%

modMTLDE <- stan_glmer(paste("MTLD", e1model_string), data=e1ld)
summary(modMTLDE) #
p_direction(modMTLDE, effects="all") # EL 78.5% AA 89.2% RR 86.6% genderM 87.8% parent_ed 91.5%

tokens_modE <- stan_glmer(paste("tokens", e1model_string),  data=e1ld) 
summary(tokens_modE) # condition 54.4 
get_stan_glmer_reporting_values(tokens_modE, 'parent_ed') # SHOULD REPORT
p_direction(tokens_modE, effects="all") # RR 75.7% parent_ed 95.1%

# predict word types
types_modE <- stan_glmer(paste("types", e1model_string), data=e1ld) 
summary(types_modE) 
p_direction(types_modE, effects="all") # EL 87.2% AA 77.7% genderM 88.3%, parent_ed 91.7% cond:AA 94.5%
get_stan_glmer_reporting_values(types_modE, 'parent_ed') 
get_stan_glmer_reporting_values(types_modE, 'conditionexp:AA')

# predict # of conversational turns
modCT <- stan_glmer(Conversational_Turns ~ condition * age + (1|video), data=e1ld)
summary(modCT) 
get_stan_glmer_reporting_values(modCT, "conditionexp") # pd = .92
# E1 CT: exp early significant (+ effect)
# E2 CT: age nearly significany (+ effect)
```

@@

We also conducted similar regressions predicting the number of word tokens and types, finding an effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`]), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence interval (conf. int.): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, 95% conf. int.: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).

@@

e1tokens <- ggplot(e1_tok, aes(x=Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ld, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Number of Word Tokens") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ") + small_text

@@

e2tokens <- ggplot(e2tok, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2data, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Number of Word Tokens") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ") + small_text

@@

model_string = "~ Condition * age + (1| Video)" # + gender + parent_ed
# Total number of bids
e1bids_mod <- stan_glmer(paste("bids_tot", model_string), data = e1ja) # 
summary(e1bids_mod) 
e1bids = get_stan_glmer_reporting_values(e1bids_mod, "ConditionActivity Video") # 2.59

@@

e1tja_mod <- stan_lmer(paste("total_ja", model_string), data = e1ja)
summary(e1tja_mod) # NA

e1tjadur_mod <- stan_lmer(paste("total_lja", model_string), control = list(adapt_delta = 0.99), data = e1ja)
summary(e1tjadur_mod) # NA

# Episodes of passive joint attention.
e1pja_mod <- stan_lmer(paste("pja", model_string), data = e1ja)
summary(e1pja_mod) # NA

# Episodes of coordinated joint attention.
e1cja_mod <- stan_lmer(paste("cja", model_string), control = list(adapt_delta = 0.99), data = e1ja) 
summary(e1cja_mod) # NA

# Total duration of passive joint attention.
e1pja_time_mod <- stan_lmer(paste("pja_length", model_string), data = e1ja)
summary(e1pja_time_mod) # NA

# Total duration of coordinated joint attention.
e1cja_time_mod <- stan_lmer(paste("cja_length", model_string), data = e1ja)
summary(e1cja_time_mod) # NA
```

@@

# Total number of bids
e1bids_modE <- stan_glmer(paste("bids_tot", model_stringE), data = e1ja) 
summary(e1bids_modE) # cond, almost gender

# Episodes of coordinated joint attention.
e1cja_modE <- stan_lmer(paste("cja", model_stringE), data = e1ja)
summary(e1cja_modE) # NA

# Episodes of passive joint attention.
e1pja_modE <- stan_lmer(paste("pja", model_stringE), data = e1ja)
summary(e1pja_modE) # condition*RR beta=1.8, RR close
get_stan_glmer_reporting_values(e1pja_modE, "RR") # -1.09, 95% CI = [-2.22,0.07] % report % posterior <0?
e1pjaE = get_stan_glmer_reporting_values(e1pja_modE, "ConditionActivity Video:RR")

# Total duration of passive joint attention.
e1pja_time_modE <- stan_lmer(paste("pja_length", model_stringE), data = e1ja)
summary(e1pja_time_modE) # NA

# Total duration of coordinated joint attention.
e1cja_time_modE <- stan_lmer(paste("cja_length", model_stringE), data = e1ja)
summary(e1cja_time_modE) # NA
```

We fit a Bayesian mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video. 
There were more bids for JA in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]). 
Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
There were no notable effects on the number of or total duration of coordinated or passive JA episodes.
Figure \@ref(fig:JA) (top) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR. 
These models included random intercepts per video. 
Of these exploratory regressions, only the regression predicting the number of passive JA episodes showed an effect involving these demographic variables: an interaction of condition and RR ($\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaE['95pLB']`,`r e1pjaE['95pUB']`]), shows that for parents in the Activity Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.

@@

e1bids <- ggplot(ms_bids1, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ja, aes(x=Condition, y=bids_tot), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Mean Bids for Joint Attention") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none") + ggtitle("Experiment 1") + small_text

@@

e1tja <- ggplot(ms_tja1, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Mean Episodes of Joint Attention") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none") + ggtitle(" ") + small_text

@@

e2_bids <- e2ja %>% group_by(Condition) %>%
  tidyboot_mean(bids)
e2bids <- ggplot(e2_bids, aes(x = Condition, y = mean, fill = str_wrap(Condition, 8))) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  labs(fill="Condition") + 
  geom_point(data=e2ja, aes(x=Condition, y=bids), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Bids for Joint Attention") + 
  scale_fill_manual(values=sol_colors) + ggthemes::theme_few() + ggtitle("Experiment 2") + small_text +
  theme(legend.position="none")
  #theme(legend.key.height=unit(1.2, "cm"), legend.text=element_text(size=9))

# total JA episodes (not currently graphed)
e2_tja <- e2ja %>% group_by(Condition) %>%
  tidyboot_mean(total_ja) 
e2tja <- ggplot(e2_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Episodes of Joint Attention") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  ggtitle(" ") + small_text + theme(legend.position="none")

e2tja_age = ggplot(e2ja, aes(x = Age, y = total_ja, group=Condition, colour=Condition)) +
  geom_point(alpha=.8) + geom_smooth(method='lm') + scale_colour_manual(values=rev(sol_colors)) +
  xlab("Age (years)") + ylab("Total Episodes of Joint Attention") +
  ggthemes::theme_few() + ggtitle(" ") + small_text + 
  theme(legend.position="bottom", legend.text=element_text(size=9), 
        legend.margin=margin(0,0,5,0),
        legend.box.margin=margin(-10,-10,-5,-10))
  #theme(legend.position="none")

@@

# Notes: 
# - including (1|sid) never works: "Error: number of levels of each grouping factor must be < number of observations", so we back off to (1|video)
# Predicting lexical diversity based on experimental condition. 
e2TTR_m <- stan_lmer(TTR ~ age * condition + (1 | video), data=e2data) 
summary(e2TTR_m) # conditionexp beta=-.1 95% CI=[-.2,0.0]
e2TTR <- get_stan_glmer_reporting_values(e2TTR_m,"conditionexp")

>>>>

```{r load-exp1-lexical-data, include=F}
e1path = "../parenting_obs_e1/"
load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting
e1_parent_ed = table(d$parent_ed)
#d <- read.csv(paste(e1path,"exp1_conditions2.csv",sep=''))
#d = read.csv("exp1_lexical_diversity_data.csv") # old one
d = read.csv("../exp1_lexical_diversityAdd.csv") # with Conversational_Turns

@@

e1_gender = table(e1ld$gender)

# rate calculations (tokens / min, words / min)
e1_dur = read.csv(paste0(e1path,"joint_attention/parenting_obs_play_duration_E1.csv"))
e1_dur <- e1_dur %>% mutate(vid_dur=video_duration_sec / 60) %>% # sec / min
  select(SID, vid_dur)
e1ld <- e1ld %>% left_join(e1_dur, by=c("sid"="SID"))

# convert types and tokens to rate: types/min and tokens/min
e1ld <- e1ld %>% 
  mutate(types = (types / vid_dur), 
         tokens = (tokens / vid_dur),
         Conversational_Turns = (Conversational_Turns / vid_dur))
```

```{r load-exp1-joint-attention-data, echo=F}
load(paste0(e1path,"joint_attention/Exp1_joint_attention_data.RData"))
d$Condition <- factor(d$Condition, levels = c("con","exp"), labels = c("No Video","Activity Video"))

@@

```{r load-exp2-lexical-data, echo=F}
e2path = "../parenting_obs_e2/"
load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
e2Age <- d %>% mutate(Age = age) %>%
  select(sid, Age)
e2_parent_ed = table(d$parent_ed) # unscaled parent_ed
#d = read.csv("exp2_lexical_diversity_data.csv")
d = read.csv("../exp2_lexical_diversityAdd.csv")
d <- d %>% left_join(e2Age, by="sid")

e2data <- d %>%
  mutate(condition = as.factor(condition), 
         gender = as.factor(gender),
         video = as.factor(video)) %>%
  select(-X.1, -X)

@@

e2_gender = table(d$gender)
e2_12to18 = nrow(subset(d, Age<1.5)) # wrong now that age is scaled ToDo
e2_18to24 = nrow(subset(d, Age>=1.5))

e2_dur = read.csv(paste0(e2path,"joint_attention/parenting_obs_play_duration_E2.csv"))
e2_dur <- e2_dur %>% mutate(vid_dur=video_duration_sec / 60) %>% # sec / min
  select(sid, vid_dur)
e2data <- e2data %>% left_join(e2_dur, by="sid")

# convert types and tokens to rate: types/min and tokens/min
e2data <- e2data %>% 
  mutate(types = (types / vid_dur), 
         tokens = (tokens / vid_dur),
         Conversational_Turns = (Conversational_Turns / vid_dur))
```

@@

### Procedure.
After providing informed consent, parents in the Activity Video condition watched the assigned activity video on a laptop with headphones.
To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played. 
Immediately following the video, each parent-child dyad was provided with the props to complete the video-guided activity that the parent had viewed. 
The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of approximately three minutes.[^2]
In the No Video condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
They were not given any additional instructions about how to use the props.

@@

A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55,0.91] for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95% CI = [-0.11,0.67] for rate of passive JA episodes (per minute); ICC = 0.66 with 95% CI = [0.32,0.85] for rate of coordinated JA episodes; ICC = 0.33 with 95% CI = [-0.11,0.67] for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 95% CI = [0.24,0.82] for rate (seconds per minute) of coordinated JA episodes.

@@

For each transcript, the words were lemmatized using ``spacy2`` [@spacy2], and the word *types* (unique words) and *tokens* (total words) were then tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity. 
Although TTR was our preregistered measure of lexical diversity as it has commonly been used, it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity [MTLD; @McCarthy2010]. 
Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here we use the value proposed by @McCarthy2010: 0.720).

@@

# predict word tokens
tokens_mod <- stan_glmer(tokens ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld) 
summary(tokens_mod)
e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 19.45
p_direction(tokens_mod, effects="all") # orchestra 89.7%

# predict word types
types_mod <- stan_glmer(types ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld)
summary(types_mod) # nothing 
p_direction(types_mod, effects="all") # condition 83%, age 92.5%..

e1_lexdiv <- e1ld %>% group_by(condition) %>%
  summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) # types=mean(types) # con=16.7, exp=18.1
```

```{r, e1ld-exploratory, echo=F, include=F}
# Predicting lexical diversity based on experimental condition, PAQ, demographics. 
e1model_string = "~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video)"
# only 54 parents completed the EPAQ
modTTRE <- stan_glmer(paste("TTR", e1model_string), data=e1ld)
summary(modTTRE) # conditionexp, RR, genderM, parent_ed 
get_stan_glmer_reporting_values(modTTRE, 'conditionexp') # -.11
p_direction(modTTRE, effects="all") # EL 75, RR 86%, parent_ed 83.5

modMTLDE <- stan_glmer(paste("MTLD", e1model_string), data=e1ld)
summary(modMTLDE) #
p_direction(modMTLDE, effects="all") # RR 81.5% genderM 88.9%

tokens_modE <- stan_glmer(paste("tokens", e1model_string),  data=e1ld) 
summary(tokens_modE) # condition 54.4 
get_stan_glmer_reporting_values(tokens_modE, 'parent_ed') # 
p_direction(tokens_modE, effects="all") # RR 71% parent_ed 90%

# predict word types
types_modE <- stan_glmer(paste("types", e1model_string), data=e1ld) 
summary(types_modE) 
p_direction(types_modE, effects="all") # EL 82.5% AA 87% genderM 93.2%, parent_ed 93.5% cond:AA 94.5%
get_stan_glmer_reporting_values(types_modE, 'parent_ed') 
get_stan_glmer_reporting_values(types_modE, 'conditionexp:AA')

# predict # of conversational turns - COULD REPORT THIS
modCT <- stan_glmer(Conversational_Turns ~ condition * age + (1|video), data=e1ld)
summary(modCT) 
get_stan_glmer_reporting_values(modCT, "conditionexp") # pd = .96 mean=2.52 [-.20,5.28]
p_direction(modCT, effects="all")
# E1 CT: exp early significant (+ effect)
# E2 CT: age nearly significant (+ effect)
```

@@

We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`]), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence interval (conf. int.): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, 95% conf. int.: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).

@@

e1tokens <- ggplot(e1_tok, aes(x=Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ld, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Mean Word Tokens per Minute") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ") + small_text

@@

e2tokens <- ggplot(e2tok, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2data, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Mean Word Tokens per Minute") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ") + small_text

@@

model_string = "~ Condition * age + (1| Video)" # + gender + parent_ed
# Total number of bids
e1bids_mod <- stan_glmer(paste("bids_tot", model_string), data = e1ja) # 
summary(e1bids_mod) 
e1bids = get_stan_glmer_reporting_values(e1bids_mod, "ConditionActivity Video") # .72
p_direction(e1bids_mod, effects="all")

@@

e1tja_mod <- stan_lmer(paste("total_ja", model_string), data = e1ja)
summary(e1tja_mod) # NA
p_direction(e1tja_mod, effects="all")

e1tjadur_mod <- stan_lmer(paste("total_lja", model_string), control = list(adapt_delta = 0.99), data = e1ja)
summary(e1tjadur_mod) # NA
p_direction(e1tjadur_mod, effects="all") # condition 91%

# Episodes of passive joint attention.
e1pja_mod <- stan_lmer(paste("pja", model_string), data = e1ja)
summary(e1pja_mod) # NA
p_direction(e1pja_mod, effects="all") # condition 84.5%

# Episodes of coordinated joint attention.
e1cja_mod <- stan_lmer(paste("cja", model_string), control = list(adapt_delta = 0.99), data = e1ja) 
summary(e1cja_mod) # NA
p_direction(e1cja_mod, effects="all") # condition 80%

# Total duration of passive joint attention.
e1pja_time_mod <- stan_lmer(paste("pja_length", model_string), data = e1ja)
summary(e1pja_time_mod) # NA
p_direction(e1pja_time_mod, effects="all") # condition 85.7%

# Total duration of coordinated joint attention.
e1cja_time_mod <- stan_lmer(paste("cja_length", model_string), data = e1ja)
summary(e1cja_time_mod) # NA
p_direction(e1cja_time_mod, effects="all") # cond*age 85%
```

We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video. 
Parents' bid rate was greater in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]). 
Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA (seconds per minute of play).
There were no notable effects on the rate of episodes nor on the time spent in coordinated or passive JA episodes.
Figure \@ref(fig:JA) (top) shows the mean rate of bids and episodes of JA by condition in Experiment 1.

@@

# Rate of parental bids
e1bids_modE <- stan_glmer(paste("bids_tot", model_stringE), data = e1ja) 
summary(e1bids_modE) # cond, gender 
e1bidsE = get_stan_glmer_reporting_values(e1bids_modE, "genderM") # .73 [.11,1.36] REPORT 
p_direction(e1bids_modE, effects="all")

# Episodes of coordinated joint attention.
e1cja_modE <- stan_lmer(paste("cja", model_stringE), data = e1ja)
summary(e1cja_modE) # NA
p_direction(e1cja_modE, effects="all") # RR 86% parent_ed 89%

# Episodes of passive joint attention.
e1pja_modE <- stan_lmer(paste("pja", model_stringE), data = e1ja)
summary(e1pja_modE) # condition*RR beta=1.8, RR close
e1pjaRR = get_stan_glmer_reporting_values(e1pja_modE, "RR") # -.34, 95% CI = [-.65,-.02]  REPORT
#e1pja_parent_ed = get_stan_glmer_reporting_values(e1pja_modE, "parent_ed") # -.23 [-.47,.02] pd=.97 REPORT?
e1pjaE = get_stan_glmer_reporting_values(e1pja_modE, "ConditionActivity Video:RR") # .60 [.14,1.05]
p_direction(e1pja_modE, effects="all")

# Total duration of passive joint attention.
e1pja_time_modE <- stan_lmer(paste("pja_length", model_stringE), data = e1ja)
summary(e1pja_time_modE) # NA
p_direction(e1pja_time_mod, effects="all") # condition 85.7%

# Total duration of coordinated joint attention.
e1cja_time_modE <- stan_lmer(paste("cja_length", model_stringE), data = e1ja)
summary(e1cja_time_modE) # NA
p_direction(e1cja_time_mod, effects="all") # condition 85.1%
```

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR. 
These models included random intercepts per video. 
Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale a lower rate of passive JA episodes ($\beta=`r e1pjaRR["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaRR['95pLB']`,`r e1pjaRR['95pUB']`]).
However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR:  $\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaE['95pLB']`,`r e1pjaE['95pUB']`]).

@@

e1bids <- ggplot(ms_bids1, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ja, aes(x=Condition, y=bids_tot), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Parental Bids for JA per Minute") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none") + ggtitle("Experiment 1") + small_text

@@

e1tja <- ggplot(ms_tja1, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Episodes of JA per Minute") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none") + ggtitle(" ") + small_text

@@

e2_bids <- e2ja %>% group_by(Condition) %>%
  tidyboot_mean(bids)
e2bids <- ggplot(e2_bids, aes(x = Condition, y = mean, fill = str_wrap(Condition, 8))) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  labs(fill="Condition") + 
  geom_point(data=e2ja, aes(x=Condition, y=bids), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Parental Bids for JA per Minute") + 
  scale_fill_manual(values=sol_colors) + ggthemes::theme_few() + ggtitle("Experiment 2") + small_text +
  theme(legend.position="none")
  #theme(legend.key.height=unit(1.2, "cm"), legend.text=element_text(size=9))

# total JA episodes (not currently graphed)
e2_tja <- e2ja %>% group_by(Condition) %>%
  tidyboot_mean(total_ja) 
e2tja <- ggplot(e2_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Episodes of JA per Minute") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  ggtitle(" ") + small_text + theme(legend.position="none")

e2tja_age = ggplot(e2ja, aes(x = Age, y = total_ja, group=Condition, colour=Condition)) +
  geom_point(alpha=.8) + geom_smooth(method='lm') + scale_colour_manual(values=rev(sol_colors)) +
  xlab("Age (years)") + ylab("Episodes of JA per Minute") +
  ggthemes::theme_few() + ggtitle(" ") + small_text + 
  theme(legend.position="bottom", legend.text=element_text(size=9), 
        legend.margin=margin(0,0,5,0),
        legend.box.margin=margin(-10,-10,-5,-10))
  #theme(legend.position="none")

@@

# Notes: 
# - including (1|sid) never works: "Error: number of levels of each grouping factor must be < number of observations", so we back off to (1|video)
# Predicting lexical diversity based on experimental condition. 
e2TTR_m <- stan_lmer(TTR ~ age * condition + (1 | video), data=e2data) 
summary(e2TTR_m) # conditionexp beta=-.1 95% CI=[-.2,0.0]
e2TTR <- get_stan_glmer_reporting_values(e2TTR_m,"conditionexp") # -.09 [-.15,-.04]
p_direction(e2TTR_m, effects="all") # age 85.6% age:cond 78%

# predict word tokens
e2tokens_m <- stan_lmer(log(tokens) ~ age * condition + (1 | video), data=e2data)
summary(e2tokens_m) # NA 
print(e2tokens_m, digits=2)
p_direction(e2tokens_m, effects="all") 
#launch_shinystan(e2tokens_m, ppd = FALSE)
#summary(e2tokens_m, 
#        pars = c("(Intercept)", "age", "conditionexp", "age:conditionexp"),
#        probs = c(0.025, 0.975),
#        digits = 2)
#plot(e2tokens_m)
#prior_summary(object = e2tokens_m)
get_stan_glmer_reporting_values(e2tokens_m,"conditionexp")
